Vegetation regrowth/encroachment (gjengroing)

### 2023-08-29 DRAFT_functional_plant_indicators_natopen.Rmd
natopen markdown continued

Grazing_mowing, ANO:
```{r}
#summary(res.seminat$kartleggingsenhet_1m2)
#length(unique(res.seminat$kartleggingsenhet_1m2))
# 19 NiN-types, of which T41-C-1 has 0 observations, and T32 & T34 as main types don't have a reference -> so, 16 NiN-Types to plot
#colnames(seminat.ref.cov[['Light']])

### Grazing_mowing
par(mfrow=c(2,4))
## T32s
# T32-C-1
plot(density( as.matrix(seminat.ref.cov[['Grazing_mowing']][,"T32-C1C2"]) ,na.rm=T),
     xlim=c(1,8), type="l", main='T32-C1',xlab='Grazing_mowing value')
points(density(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T32-C-1",]$original,na.rm=T),
       type="l", col="red")
points(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T32-C-1",]$original,
       rep(0,length(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T32-C-1",]$original)),
       col="red")

# T32-C-2
plot(density( as.matrix(seminat.ref.cov[['Grazing_mowing']][,"T32-C1C2"]) ,na.rm=T),
     xlim=c(1,8), type="l", main='T32-C2',xlab='Grazing_mowing value')
points(density(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T32-C-2",]$original,na.rm=T),
       type="l", col="red")
points(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T32-C-2",]$original,
       rep(0,length(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T32-C-2",]$original)),
       col="red")

# T32-C-3
plot(density( as.matrix(seminat.ref.cov[['Grazing_mowing']][,"T32-C3C4"]) ,na.rm=T),
     xlim=c(1,8), type="l", main='T32-C3',xlab='Grazing_mowing value')
points(density(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T32-C-3",]$original,na.rm=T),
       type="l", col="red")
points(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T32-C-3",]$original,
       rep(0,length(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T32-C-3",]$original)),
       col="red")

# T32-C-4
plot(density( as.matrix(seminat.ref.cov[['Grazing_mowing']][,"T32-C3C4"]) ,na.rm=T),
     xlim=c(1,8), type="l", main='T32-C4',xlab='Grazing_mowing value')
points(density(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T32-C-4",]$original,na.rm=T),
       type="l", col="red")
points(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T32-C-4",]$original,
       rep(0,length(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T32-C-4",]$original)),
       col="red")

# T32-C-5
plot(density( as.matrix(seminat.ref.cov[['Grazing_mowing']][,c("T32-C5C20a","T32-C5C20b")]) ,na.rm=T),
     xlim=c(1,8), type="l", main='T32-C5',xlab='Grazing_mowing value')
points(density(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T32-C-5",]$original,na.rm=T),
       type="l", col="red")
points(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T32-C-5",]$original,
       rep(0,length(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T32-C-5",]$original)),
       col="red")

# T32-C-6
plot(density( as.matrix(seminat.ref.cov[['Grazing_mowing']][,c("T32-C21C6a","T32-C21C6b")]) ,na.rm=T),
     xlim=c(1,8), type="l", main='T32-C6',xlab='Grazing_mowing value')
points(density(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T32-C-6",]$original,na.rm=T),
       type="l", col="red")
points(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T32-C-6",]$original,
       rep(0,length(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T32-C-6",]$original)),
       col="red")

# T32-C-9
plot(density( as.matrix(seminat.ref.cov[['Grazing_mowing']][,c("T32-C9a","T32-C9b")]) ,na.rm=T),
     xlim=c(1,8), type="l", main='T32-C9',xlab='Grazing_mowing value')
points(density(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T32-C-9",]$original,na.rm=T),
       type="l", col="red")
points(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T32-C-9",]$original,
       rep(0,length(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T32-C-9",]$original)),
       col="red")

# T32-C-10
plot(density( as.matrix(seminat.ref.cov[['Grazing_mowing']][,c("T32-C10a","T32-C10b")]) ,na.rm=T),
     xlim=c(1,8), type="l", main='T32-C10',xlab='Grazing_mowing value')
points(density(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T32-C-10",]$original,na.rm=T),
       type="l", col="red")
points(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T32-C-10",]$original,
       rep(0,length(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T32-C-10",]$original)),
       col="red")

par(mfrow=c(2,4))
# T32-C-15
plot(density( as.matrix(seminat.ref.cov[['Grazing_mowing']][,c("T32-C15")]) ,na.rm=T),
     xlim=c(1,8), type="l", main='T32-C15',xlab='Grazing_mowing value')
#points(density(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T32-C-15",]$original,na.rm=T),
#       type="l", col="red")
points(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T32-C-15",]$original,
       rep(0,length(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T32-C-15",]$original)),
       col="red")

# T32-C-20
plot(density( as.matrix(seminat.ref.cov[['Grazing_mowing']][,c("T32-C5C20a","T32-C5C20b")]) ,na.rm=T),
     xlim=c(1,8), type="l", main='T32-C20',xlab='Grazing_mowing value')
points(density(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T32-C-20",]$original,na.rm=T),
       type="l", col="red")
points(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T32-C-20",]$original,
       rep(0,length(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T32-C-20",]$original)),
       col="red")

## V10s
# V10-C-1
plot(density( as.matrix(seminat.ref.cov[['Grazing_mowing']][,"V10-C1C2"]) ,na.rm=T),
     xlim=c(1,8), type="l", main='V10-C1',xlab='Grazing_mowing value')
points(density(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="V10-C-1",]$original,na.rm=T),
       type="l", col="red")
points(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="V10-C-1",]$original,
       rep(0,length(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="V10-C-1",]$original)),
       col="red")

# V10-C-3
plot(density( as.matrix(seminat.ref.cov[['Grazing_mowing']][,"V10-C3"]) ,na.rm=T),
     xlim=c(1,8), type="l", main='V10-C3',xlab='Grazing_mowing value')
#points(density(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="V10-C-3",]$original,na.rm=T),
#       type="l", col="red")
points(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="V10-C-3",]$original,
       rep(0,length(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="V10-C-3",]$original)),
       col="red")

## T34s
# T34-C-1
plot(density( as.matrix(seminat.ref.cov[['Grazing_mowing']][,"T34-C1"]) ,na.rm=T),
     xlim=c(1,8), type="l", main='T34-C1',xlab='Grazing_mowing value')
points(density(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T34-C-1",]$original,na.rm=T),
       type="l", col="red")
points(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T34-C-1",]$original,
       rep(0,length(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T34-C-1",]$original)),
       col="red")

# T34-C-2
plot(density( as.matrix(seminat.ref.cov[['Grazing_mowing']][,c("T34-C2a","T34-C2b","T34-C2c")]) ,na.rm=T),
     xlim=c(1,8), type="l", main='T34-C2',xlab='Grazing_mowing value')
points(density(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T34-C-2",]$original,na.rm=T),
       type="l", col="red")
points(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T34-C-2",]$original,
       rep(0,length(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T34-C-2",]$original)),
       col="red")

# T34-C-4
plot(density( as.matrix(seminat.ref.cov[['Grazing_mowing']][,c("T34-C4a","T34-C4b","T34-C4c","T34-C4d")]) ,na.rm=T),
     xlim=c(1,8), type="l", main='T34-C4',xlab='Grazing_mowing value')
#points(density(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T34-C-4",]$original,na.rm=T),
#       type="l", col="red")
points(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T34-C-4",]$original,
       rep(0,length(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T34-C-4",]$original)),
       col="red")

## T41
plot(density( as.matrix(seminat.ref.cov[['Grazing_mowing']][,c("T41a","T41b")]) ,na.rm=T),
     xlim=c(1,8), type="l", main='T41',xlab='Grazing_mowing value')
points(density(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T41",]$original,na.rm=T),
       type="l", col="red")
points(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T41",]$original,
       rep(0,length(res.seminat.ANO[res.seminat.ANO$fp_ind=="Grazing_mowing1" & res.seminat.ANO$kartleggingsenhet_1m2=="T41",]$original)),
       col="red")
legend("topleft", legend=c("reference","field data"), pch=c(NA,1), lty=1, col=c("black","red"))

@@

Nitrogen, ASO
```{r}

#summary(res.seminat.ASO$NiN_grunntype)
#length(levels(res.seminat.ASO$NiN_grunntype))
# 12 NiN-types, of which C-13 and C-2 have 0 observations -> so, 10 NiN-Types to plot
#colnames(seminat.ref.cov[['Nitrogen']])

### Nitrogen
par(mfrow=c(3,4))
# T32-C-1
plot(density( as.matrix(seminat.ref.cov[['Nitrogen']][,"T32-C1C2"]) ,na.rm=T),
     xlim=c(1,8), type="l", main='T32-C1',xlab='Nitrogen value')
points(density(res.seminat.ASO[res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$NiN_grunntype=="T32-C-1",]$original,na.rm=T),
       type="l", col="red")
points(res.seminat.ASO[res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$NiN_grunntype=="T32-C-1",]$original,
       rep(0,length(res.seminat.ASO[res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$NiN_grunntype=="T32-C-1",]$original)),
       col="red")

# T32-C-3
plot(density( as.matrix(seminat.ref.cov[['Nitrogen']][,"T32-C3C4"]) ,na.rm=T),
     xlim=c(1,8), type="l", main='T32-C3',xlab='Nitrogen value')
points(density(res.seminat.ASO[res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$NiN_grunntype=="T32-C-3",]$original,na.rm=T),
       type="l", col="red")
points(res.seminat.ASO[res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$NiN_grunntype=="T32-C-3",]$original,
       rep(0,length(res.seminat.ASO[res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$NiN_grunntype=="T32-C-3",]$original)),
       col="red")

# T32-C-4
plot(density( as.matrix(seminat.ref.cov[['Nitrogen']][,"T32-C3C4"]) ,na.rm=T),
     xlim=c(1,8), type="l", main='T32-C4',xlab='Nitrogen value')
points(density(res.seminat.ASO[res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$NiN_grunntype=="T32-C-4",]$original,na.rm=T),
       type="l", col="red")
points(res.seminat.ASO[res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$NiN_grunntype=="T32-C-4",]$original,
       rep(0,length(res.seminat.ASO[res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$NiN_grunntype=="T32-C-4",]$original)),
       col="red")

# T32-C-5
plot(density( as.matrix(seminat.ref.cov[['Nitrogen']][,c("T32-C5C20a","T32-C5C20b")]) ,na.rm=T),
     xlim=c(1,8), type="l", main='T32-C5',xlab='Nitrogen value')
points(density(res.seminat.ASO[res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$NiN_grunntype=="T32-C-5",]$original,na.rm=T),
       type="l", col="red")
points(res.seminat.ASO[res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$NiN_grunntype=="T32-C-5",]$original,
       rep(0,length(res.seminat.ASO[res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$NiN_grunntype=="T32-C-5",]$original)),
       col="red")

# T32-C-6
plot(density( as.matrix(seminat.ref.cov[['Nitrogen']][,c("T32-C21C6a","T32-C21C6b")]) ,na.rm=T),
     xlim=c(1,8), type="l", main='T32-C6',xlab='Nitrogen value')
points(density(res.seminat.ASO[res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$NiN_grunntype=="T32-C-6",]$original,na.rm=T),
       type="l", col="red")
points(res.seminat.ASO[res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$NiN_grunntype=="T32-C-6",]$original,
       rep(0,length(res.seminat.ASO[res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$NiN_grunntype=="T32-C-6",]$original)),
       col="red")

# T32-C-7
plot(density( as.matrix(seminat.ref.cov[['Nitrogen']][,c("T32-C7C8")]) ,na.rm=T),
     xlim=c(1,8), type="l", main='T32-C7',xlab='Nitrogen value')
#points(density(res.seminat.ASO[res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$NiN_grunntype=="T32-C-7",]$original,na.rm=T),
#       type="l", col="red")
points(res.seminat.ASO[res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$NiN_grunntype=="T32-C-7",]$original,
       rep(0,length(res.seminat.ASO[res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$NiN_grunntype=="T32-C-7",]$original)),
       col="red")

# T32-C-8
plot(density( as.matrix(seminat.ref.cov[['Nitrogen']][,c("T32-C7C8")]) ,na.rm=T),
     xlim=c(1,8), type="l", main='T32-C8',xlab='Nitrogen value')
points(density(res.seminat.ASO[res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$NiN_grunntype=="T32-C-8",]$original,na.rm=T),
       type="l", col="red")
points(res.seminat.ASO[res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$NiN_grunntype=="T32-C-8",]$original,
       rep(0,length(res.seminat.ASO[res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$NiN_grunntype=="T32-C-8",]$original)),
       col="red")

# T32-C-9
plot(density( as.matrix(seminat.ref.cov[['Nitrogen']][,c("T32-C9a","T32-C9b")]) ,na.rm=T),
     xlim=c(1,8), type="l", main='T32-C9',xlab='Nitrogen value')
#points(density(res.seminat.ASO[res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$NiN_grunntype=="T32-C-9",]$original,na.rm=T),
#       type="l", col="red")
points(res.seminat.ASO[res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$NiN_grunntype=="T32-C-9",]$original,
       rep(0,length(res.seminat.ASO[res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$NiN_grunntype=="T32-C-9",]$original)),
       col="red")

# T32-C-10
plot(density( as.matrix(seminat.ref.cov[['Nitrogen']][,c("T32-C10a","T32-C10b")]) ,na.rm=T),
     xlim=c(1,8), type="l", main='T32-C10',xlab='Nitrogen value')
#points(density(res.seminat.ASO[res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$NiN_grunntype=="T32-C-10",]$original,na.rm=T),
#       type="l", col="red")
points(res.seminat.ASO[res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$NiN_grunntype=="T32-C-10",]$original,
       rep(0,length(res.seminat.ASO[res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$NiN_grunntype=="T32-C-10",]$original)),
       col="red")

# T32-C-20
plot(density( as.matrix(seminat.ref.cov[['Nitrogen']][,c("T32-C5C20a","T32-C5C20b")]) ,na.rm=T),
     xlim=c(1,8), type="l", main='T32-C20',xlab='Nitrogen value')
points(density(res.seminat.ASO[res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$NiN_grunntype=="T32-C-20",]$original,na.rm=T),
       type="l", col="red")
points(res.seminat.ASO[res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$NiN_grunntype=="T32-C-20",]$original,
       rep(0,length(res.seminat.ASO[res.seminat.ASO$fp_ind=="Nitrogen2" & res.seminat.ASO$NiN_grunntype=="T32-C-20",]$original)),
       col="red")

legend("topleft", legend=c("reference","field data"), pch=c(NA,1), lty=1, col=c("black","red"))

>>>>

CSR-R, ANO:
```{r}
# summary(res.natopen.ANO$kartleggingsenhet_1m2)
# 15 NiN-types, of which T2, T13 & T18 as main types don't have a reference
# many T13-types (rasmark) have too few vascular plants in the reference lists for getting a reference distribution
# C1, C2 and C10 in the ANO data have none
#-> so, 9 NiN-Types to plot

x11()
par(mfrow=c(3,3))

for ( i in sort(unique(res.natopen.ANO$kartleggingsenhet_1m2)[-c(2,8,9,12,13,15)]) ) {

  tryCatch({

    plot(density( as.matrix(natopen.ref.cov[['RR']][,i]) ,na.rm=T),
         xlim=c(0,1), ylim=c(0,10), type="l", main=i,xlab='CSR-R value')
    points(density(res.natopen.ANO[res.natopen.ANO$fp_ind=="RR1" & res.natopen.ANO$kartleggingsenhet_1m2==i,]$original,na.rm=T),
           type="l", col="red")
    points(res.natopen.ANO[res.natopen.ANO$fp_ind=="RR1" & res.natopen.ANO$kartleggingsenhet_1m2==i,]$original,
           rep(0,length(res.natopen.ANO[res.natopen.ANO$fp_ind=="RR1" & res.natopen.ANO$kartleggingsenhet_1m2==i,]$original)),
           col="red")

  }, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})

}
legend("topright", legend=c("reference","field data"), pch=c(NULL,1), lty=1, col=c("black","red"))

@@

Nitrogen, GRUK
```{r}

# only two NiN types in GRUK, T2-C-7 and T2-C-8
par(mfrow=c(1,2))

for ( i in unique(res.natopen.GRUK$Kartleggingsenhet) ) {

  tryCatch({

    plot(density( as.matrix(natopen.ref.cov[['Nitrogen']][,i]) ,na.rm=T),
         xlim=c(1,9), ylim=c(0,2), type="l", main=i,xlab='Nitrogen value')
    points(density(res.natopen.GRUK[res.natopen.GRUK$fp_ind=="Nitrogen1" & res.natopen.GRUK$Kartleggingsenhet==i,]$original,na.rm=T),
           type="l", col="red")
    points(res.natopen.GRUK[res.natopen.GRUK$fp_ind=="Nitrogen1" & res.natopen.GRUK$Kartleggingsenhet==i,]$original,
           rep(0,length(res.natopen.GRUK[res.natopen.GRUK$fp_ind=="Nitrogen1" & res.natopen.GRUK$Kartleggingsenhet==i,]$original)),
           col="red")

  }, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})

}
legend("topright", legend=c("reference","field data"), pch=c(NA,1), lty=1, col=c("black","red"))
